Coherent optical association of atoms into a single molecule

### 2020-11-14 paper.tex
Update on Overleaf.

\begin{abstract}
  We report on coherent association
  of atoms into a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69\mathrm{\%}$.
  The molecules have a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
  and are created with higher than $60\mathrm{\%}$ probability in the motional ground state.
  This technique does not rely on narrow excited-state lines or Feshbach resonances
  and may allow a wide range of molecular species to be assembled atom-by-atom.
\end{abstract}

>>>>

\begin{abstract}
  We report on coherent association
  of atoms into a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69\mathrm{\%}$.
  The molecules have a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
  and are created with higher than $60\mathrm{\%}$ probability in the motional ground state.
  This technique does not rely on Feshbach resonances or narrow excited-state lines 
  and may allow a wide range of molecular species to be assembled atom-by-atom.
\end{abstract}
